Supplementary Report for the article *Functional diversity can facilitate the collapse of an undesirable ecosystem state*

### 2022-10-05 experiments/2_supplement/supplement.Rmd
Update supplement.Rmd

### What causes variation in response to oxygen diffusivity (SB)?

@@

### What causes variation in response to oxygen diffusivity (CB-SB)?

In the ecosystem shown in Figure \@ref(fig:max-tol5), where CB and SB each contained only one strain with very high tolerance, there was large variation in state variables along the oxygen diffusivity gradient at values less than about -6.5. To examine what might be causing this, we simulated the ecosystem at a constant oxygen diffusivity of $log_{10}$ oxygen diffusivity of -6 (Figure \@ref(fig:CBSB-maxtol-dyn1)). We see that the dynamics are qualitatively different from other cases in which there is a stable state reached in such a simulation (Figure \@ref(fig:sb-div-effect4)). It appears that the SB strain with high tolerance is able to initiate a transition to an anoxic state, but is not able to create a stable anoxic state.

@@

(ref:CBSB-maxtol-dyn1) Temporal dynamics of an ecosystem with a single CB strain with high tolerance and a single SB strain with high tolerance, the same one as in Figure \@ref(fig:max-tol5) simulated with constant $log_{10}(oxygen diffusivity) of -6.

>>>>

### What causes the variation in response to oxygen diffusivity (SB)?

@@

### What causes the variation in response to oxygen diffusivity (CB-SB)?

In the ecosystem shown in Figure \@ref(fig:max-tol5), where CB and SB each contained only one strain with very high tolerance, there was large variation in state variables along the oxygen diffusivity gradient at values less than about -6.5. To examine what might be causing this, we simulated the ecosystem at a constant oxygen diffusivity of $log_{10}$ oxygen diffusivity of -7 (Figure \@ref(fig:CBSB-maxtol-dyn1)). We see that the dynamics are qualitatively different from other cases in which there is a stable state reached in such a simulation (Figure \@ref(fig:sb-div-effect4)). It appears that the SB strain with high tolerance is able to initiate a transition to an anoxic state, but is not able to create a stable anoxic state.

@@

(ref:CBSB-maxtol-dyn1) Temporal dynamics of an ecosystem with a single CB strain with high tolerance and a single SB strain with high tolerance, the same one as in Figure \@ref(fig:max-tol5) simulated with constant $log_{10}(oxygen diffusivity)$ of -6.
